Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-23 paper/paper.Rmd
Add effect size plot

The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest. Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically underpowered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if it was judged to be closer to the original:
\%`r round(mean(d$replicated_TA[d$high_fidelity]), digits=2)` 
vs. 
\%`r round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`.
There were small numerical effects of being run on Mechanical Turk (
\%`r round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)` 
vs. 
\%`r round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`. 
) and having open materials (
\%`r round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)` 
vs. 
\%`r round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`), though we do not believe these differences are interpretable given our sample size.

@@

Flag: Original effect size not given for auc?

```{r}
d$original_ES <- as.numeric(gsub(".*=(.*)","\\1", d$original_ES_text))
#Ensure that effect size is given in same units... Make beautiful ci chart here...
```

@@

```{r, fig.height=9, fig.width=6}
library(png)
layout(matrix(1:24,nr=6,byr=T))
for (key in project_plan$project_key) {
  orig <- readPNG(paste0("../figures/",key,"-original.png"))
  rep <- readPNG(paste0("../figures/",key,"-replication.png"))

  par(mai=c(0,0,0,0))
  plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
  rasterImage(orig, 0, 0, 100, 100, interpolate=FALSE)

  plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
  rasterImage(rep, 0, 0, 100, 100, interpolate=FALSE)

}
```

@@

- key statistic in original 
-

##

@@

<!-- All materials that are needed for class to implement -->
<!-- Email templates -->
<!-- Spreadsheets -->
<!-- TA/prof auditing processes --

>>>>

The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest. Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically underpowered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if it was judged to be closer to the original:
`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
vs. 
`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%.
There were small numerical effects of being run on Mechanical Turk (
`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\%
vs. 
`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%. 
) and having open materials (
`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
vs. 
`r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.

@@

```{r}
# Note that the sofer paper is off the charts (d > 16) and excluded
ggplot(d,aes(x=original_ES_d,y=rep_es, 
             color=d$replicated_TA_factor)) +
  geom_jitter(height=0, width=.2) +
  geom_vline(xintercept=c(0.2), lty = 5) +
  geom_vline(xintercept=c(0.5), lty = 2) +
  geom_vline(xintercept=c(0.8), lty = 3) +
  # geom_hline(yintercept=c(0.2), lty = 5) +
  # geom_hline(yintercept=c(0.5), lty = 2) +
  # geom_hline(yintercept=c(0.8), lty = 3) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  xlab("Original effect size (cohen's d)") + 
  ylab("Replication effect size (cohen's d)") + 
  theme_bw() + 
  scale_color_solarized(name = "Subjective replication rating") + 
  xlim(0, 4) +
  ylim(0, 4) +
  theme(legend.position = "bottom")

# Make beautiful ci chart here...

```

@@

```{r, fig.height=9, fig.width=6}
# library(png)
# layout(matrix(1:24,nr=6,byr=T))
# for (key in project_plan$project_key) {
#   orig <- readPNG(paste0("../figures/",key,"-original.png"))
#   rep <- readPNG(paste0("../figures/",key,"-replication.png"))
# 
#   par(mai=c(0,0,0,0))
#   plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
#   rasterImage(orig, 0, 0, 100, 100, interpolate=FALSE)
# 
#   plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
#   rasterImage(rep, 0, 0, 100, 100, interpolate=FALSE)
# 
# }
```

@@

- key statistic in original

@@

<!-- All materials that are needed for class to implement -->
<!-- Email templates -->
<!-- Spreadsheets -->
<!-- TA/prof auditing processes -->
